---
title: "mattdancho"
format: html
---

<https://www.youtube.com/watch?v=Otb340lyiAQ>

<https://www.r-bloggers.com/2023/12/introduction-to-a-b-testing-in-r-for-marketing-analytics/>

### A/B Testing

Business Science
Lab 89: Causal Inference in R
Part 1: A/B Testing (Beginner)
Hotel Bookings and Adspend Analysis

Questions:

1. Does Adspend increase bookings?

2. By how much? Was there a Return on Adspend (ROAS)?

Can we create an experiment?

- Yes. We can work with Marketing to design Google Ads for keyword searches (e.g. travel to Chicago)

- We can set Treatment and Control by Geography, which allows us to match bookings through the experiment

- This is called GeoExperimentation: Where the treatment is administered at the geo-level

```{r message=FALSE}
# Load libraries
library(tidyverse)
library(infer)
library(timetk)
library(plotly)
library(vroom)
```

Data & Experiemnt Setup

- period = 0: Pre/Post Experiment, 1: During Experiment

- assignment = "control" part of the control group, "treatment" part of the treatment group

- treatment = 0: No Adspend, 1: Adspend

- geo: Segmentation was performed by geography

- bookings: Target feature

- cost: Adspend

```{r}
hotel_bookings_raw_tbl <- vroom("hotel_bookings_geo_experiment.csv")

hotel_bookings_raw_tbl
```

```{r}
PRE_INTERVENTION <- c("2015-01-05", "2015-02-15") |> as_date()
POST_INTERVENTION <- c("2015-02-16", "2015-03-15") |> as_date()
```

### This from the r-bloggers article

```{r}
bookings_by_assignment_over_time_tbl <- hotel_bookings_raw_tbl |> 
  group_by(assignment) |> 
  summarise_by_time(
    bookings = sum(bookings),
    cost = sum(cost),
    .by = "day"
  ) |> 
  ungroup()

bookings_by_assignment_over_time_tbl |> 
  group_by(assignment) |> 
  plot_time_series(
    date, bookings,
    .color_var = assignment,
    .interactive = FALSE,
    .title = "Adspend Effect"
  ) +
  annotate(
    "rect",
    xmin = as_date("2015-02-16"),
    xmax = as_date("2015-03-15"),
    ymin = -Inf,
    ymax = Inf,
    alpha = 0.2,
    fill = "blue"
  )
```


Split data into pre and experiment

```{r}
pre_intervention_only_tbl <- hotel_bookings_raw_tbl |> 
  filter_by_time(.start_date = PRE_INTERVENTION[1], .end_date = PRE_INTERVENTION[2])

experiment_only_tbl <- hotel_bookings_raw_tbl |> 
  filter_by_time(.start_date = POST_INTERVENTION[1], .end_date = POST_INTERVENTION[2])
```

### Data Exploration

Check Balance & Sample Size

- Is balanced?

- Sample size > 30?

```{r}
pre_intervention_only_tbl |> count(assignment)

```

```{r}
experiment_only_tbl |> count(assignment)
```

Check Sales Distribution

- Is balanced?

```{r}
pre_intervention_only_tbl |> 
  group_by(assignment) |> 
  summarise(bookings = sum(bookings))
```

```{r}
experiment_only_tbl |> 
  group_by(assignment) |> 
  summarise(bookings = sum(bookings))
```

Visualise the distribution

```{r}
experiment_only_tbl |> 
  ggplot(aes(x = bookings, fill = assignment)) +
  geom_density(colour = "white", alpha = 0.75) +
  theme_minimal()
```

Booking Summary

```{r}
summary_experiment_tbl <- experiment_only_tbl |> 
  select(assignment, bookings, cost) |> 
  group_by(assignment) |> 
  summarise(
    bookings_mean_before_log = mean(bookings),
    bookings_mean_log = mean(log(bookings)),
    cost_mean = mean(cost)
  )

summary_experiment_tbl
```

Visualise the log distribution

```{r}
g <- experiment_only_tbl |> 
  ggplot(aes(log(bookings), fill = assignment)) +
  geom_density(color = "white", alpha = 0.75) +
  geom_vline(aes(xintercept = bookings_mean_log), color = "black",
             linetype = "dashed", data = summary_experiment_tbl) +
  theme_minimal()

ggplotly(g)
```

### A/B Test: Difference in Means

Comparing 2 continuous groups, so use a 2-sided t-test to calculate the difference in means between the 2 populations.

```{r}
diff_in_means_data_tbl <- experiment_only_tbl |> 
  select(assignment, bookings)
```

```{r}
test_statistic_tbl <- diff_in_means_data_tbl |> 
  t_test(
    bookings ~ assignment,
    order = c("treatment", "control"),
    alternative = "two-sided"
  )

test_statistic_tbl
```

Linear Regression

If you are doing a 2-sample t-test, this is actually the same thing. More imprtantly, linear regression can help with more complex problems that contain multiple regressors.

```{r}
lm(bookings ~ assignment, data = diff_in_means_data_tbl) |> summary()
```

Average Treatment Effect (ATE)

```{r}
ate <- test_statistic_tbl$estimate

ate
```

```{r}
diff_in_means_data_tbl |> count(assignment) |> pull(n) |> pluck(2)
```

N * ATE

```{r}
bookings_increase <- 1393 * 96
```

N * ATE / COST

```{r}
ROAS <- 1393 * 96 / 50000

ROAS
```

We can see that the **Estimated ROAS is 2.67**. This means that for every dollar spent on the marketing campaign, we get $2.67 back in bookings.

### Conclusions

We have answered the two questions that we set out to answer:

1. **Does Adspend increase bookings?** Yes, there is a statistically significant effect. At a 0.10 level, we can say that there is a statistically significant effect. **The Average Treatment Effect is $96.20**.

2. **By how much? Was there a Return on Adspend (ROAS)?** Yes, there was a return on adspend. **The Estimated ROAS is 2.67**. This means that for every dollar spent on the marketing campaign, we get $2.67 back in bookings.
